\dnest~Manual

### 2016-01-14 doc/manual.tex
Note about directories

The Makefile in the Template directory should allow you to compile your model
by issuing the command {\tt make} in a terminal. The only preparation you need
to do is add the path to your \dnest~directory to an environment variable called
DNEST4\_PATH so that the compiler knows where \dnest~is on your system.
For example, on my laptop, \dnest~is located in /home/brewer/Projects/DNest4.
So I set DNEST4\_PATH to /home/brewer/Projects.

>>>>

The Makefile in the Template directory should allow you to compile your model
by issuing the command {\tt make} in a terminal. The only preparation you need
to do is add the path to your \dnest~directory to an environment variable called
DNEST4\_PATH so that the compiler knows where \dnest~is on your system.
For example, on my laptop, \dnest~is located in /home/brewer/Projects/DNest4.
So I set DNEST4\_PATH to /home/brewer/Projects.
{\bf Note: }The \#include statements in the working examples expect to find
the \dnest~header files two directories up: i.e. the working examples will only
successfully compile without modification from within the Examples directory.
However, the Template should compile from anywhere on your system provided you
have set DNEST4\_PATH correctly.
